`r params$title`

### 2019-10-14 Rmd/summary_db_cols_norman.Rmd
added supplement dir

```{r setup, echo=FALSE, include=FALSE}
prj = '/home/scharmueller/Projects/etox-base'
source(file.path(prj, 'R', 'gn_setup.R'))
```

@@

```{r echo=FALSE, message=FALSE}
## table
tab = summary_db_all(schema = schema, table = table)
## cols
l = summary_db_cols(schema = schema, table = table, cols = cols)
## names lookup table
q = "SELECT *
     FROM norman.variables"
var = read_tbl(user = DBuser, host = DBhost, port = DBport, password = DBpassword, dbname = DBetox,
               query = q)
```

>>>>

```{r setup, echo=FALSE, include=FALSE}
prj = '/home/scharmueller/Projects/standartox-build'
source(file.path(prj, 'R', 'gn_setup.R'))
```

@@

```{r echo=FALSE, message=FALSE}
## table
tab = summary_db_all(schema = schema, table = table)
## cols
l = summary_db_cols(schema = schema, table = table, cols = cols)
## names lookup table
q = "SELECT *
     FROM norman.variables"
var = read_query(user = DBuser, host = DBhost, port = DBport, password = DBpassword, dbname = DBetox,
                 query = q)
```
